Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-16 paper/paper.tex

We have made and analyzed movies out of color plots of MinD
concentration that are constructed as those in Figure~\ref{image-p},
integrated along the flattened axis, in which each frame is seperated
in simulation time by a half second. Figure~\ref{randst-plot-ave}
illustrates what is seen in these movies. In his work Mannik presents
arrow plots in which the arrow heads show the location of sequential
MinD maxima within the cell. His plots for his two abnormal cell
shapes are shown in the upper 'experiment' section of
Figure~\ref{randst-plot-ave}.  Following this, we have created plots
that show maxima that are global in space and local in time.  Of these
maxima we only show those which have greater concentration than a
chosen cutoff concentration, and also ignore maxima that appear
temporaly and spatially adjacent to preceding maxima, in order to
stop single spikes from appearing as many adjecent ones.  The overall
effect is to accurately describe what is seen in our movies.

>>>>

We have made and analyzed movies out of the MinD
concentration that are constructed as those in Figure~\ref{image-p},
integrated along the flattened axis, in which each frame is seperated
in simulation time by a half second. Figure~\ref{randst-plot-ave}
illustrates what is seen in these movies. In his work Mannik presents
arrow plots in which the arrow heads show the location of sequential
MinD maxima within the cell.  These experimental plots for two abnormal cell
shapes are shown in the upper `experiment' section of
Figure~\ref{randst-plot-ave}.  Following this, we have created plots
that show maxima that are global in space and local in time.  Of these
maxima we only show those which have greater concentration than a
chosen cutoff concentration, and also ignore maxima that appear
temporaly and spatially adjacent to preceding maxima, in order to
stop single spikes from appearing as many adjecent ones.  The overall
effect is to accurately describe what is seen in our movies.
